### 2024-09-20 manuscript.Rmd
fixed corresponding address
added motivation

note: Preprint submitted for publication

authornote: |
  Please address correspondence to: Prof. Dr. Andreas M. Brandmaier, Rüdesheimerstr. 50, 14197 Berlin, Germany. Email: andreas.brandmaier@medicalschool-berlin.de.
  The R package described in this article can be downloaded from https://github.com/brandmaier/reproducibleRchunks. The manuscript source code is available at https://github.com/brandmaier/reproducibleRchunks-manuscript. We thank Leonie Hagitte for providing comments on an earlier version of the manuscript.

@@

The `reproducibleRchunk` package allows users to make computational results in R Markdown documents automatically testable for successful reproduction (does the same script with the same data produce the same results, e.g. on a different computer and/or later in time) with minimal changes to the workflow.
There are only two things users need to change in their Markdown document if they are already using R Markdown: In the first code chunk of their document, they load the package and then change the code chunk type from `r` to `reproducibleR` for all code chunks for which reproduction should be automatically verified in future.
In `reproducibleR` chunks, all newly declared variables are automatically identified and their contents are stored in a meta data file. 
Furthermore, the code chunk itself (that is, the code syntax) is also fingerprinted and stored, such that later non-reproduction can be traced back to either changes of the code chunk or changes of the computation.
Once a document is reproduced, all computational results generated in the `reproducibleR` chunks are automatically tested for reproducibility.
Successes and failures of the reproduction attempts are displayed in a reproducibility report for each chunk.
Customizations or suppression of these reports are possible as we will demonstrate later.
A simple way to assess reproducibility of computational results would be a bitwise comparison of the entire knitted Markdown document (i.e., the resulting HTML, PDF or DOCX file) to a previous version.
Yet, a particular advantage of using `reproducibleR` chunks is that users have a fine-grained control over the stages of a data analysis or any other computation that should be checked for reproducibility. 
This allows for forensic examination of non-reproducibility; for example, finding out whether the non-reproducibility is due to changes in the data file, due to the data cleaning or the estimation of a statistical model. 
Using `reproducibleRchunks`, users can separately assess the reproducibility of each stage of a given statistical data analysis (or any other computation).
Also, not all elements of a research asset may be required to reproduce (such as the current date displayed in a presentation of results).
In the following, we will briefly demonstrate how reproduction will be checked and how successful and failed attempts are displayed by the package.
We will go into details of the mechanics of the package, and discuss potential cases of non-reproducibility and how the package will support researchers in handling these cases.

>>>>

#note: Preprint submitted for publication

authornote: |
  Please address correspondence to: Andreas M. Brandmaier, Lentzeallee 94, 14195 Berlin, Germany. Email: brandmaier@mpib-berlin.mpg.de.
  The R package described in this article can be downloaded from https://github.com/brandmaier/reproducibleRchunks. The manuscript source code is available at https://github.com/brandmaier/reproducibleRchunks-manuscript. We thank Leonie Hagitte for providing comments on an earlier version of the manuscript.

@@

When computations are repeated later in time with the goal of reproducing results computed earlier, it is hard and laborious to check whether results are identical. A typical case would be that readers download open data and open code accompanying a published report and re-run the code on their computer. In order to test whether these open materials reproduced, they would have to manually compare the newly computed results with the published manuscript -- and, often, it would not be immediately clear which results mapped to what parts of the manuscript. And even with dynamically-generated (R Markdown) documents, there is no straightforward way of checking reproducibility in an automated way.

The `reproducibleRchunk` package answers this challenge and allows users to make computational results in R Markdown documents automatically testable for successful reproduction (does the same script with the same data produce the same results, e.g. on a different computer and/or later in time) with minimal changes to users' workflows.
There are only two things users need to change in their Markdown document if they are already using R Markdown: (1) In the first code chunk of their document, they need to load the package, and (2) change the code chunk type from `r` to `reproducibleR` for every code chunk for which reproduction should be automatically verified in future.
In `reproducibleR` chunks, all newly declared variables are automatically identified and their contents are stored in a meta data file. 
Furthermore, the code chunk itself (that is, the code syntax) is also fingerprinted and stored, such that later non-reproduction can be traced back to either changes of the code chunk or changes of the computation.
Once a document is reproduced, all computational results generated in the `reproducibleR` chunks are automatically tested for reproducibility.
Successes and failures of the reproduction attempts are displayed in a reproducibility report for each chunk.
Customizations or suppression of these reports are possible as we will demonstrate later.
A simple way to assess reproducibility of computational results would be a bitwise comparison of the entire knitted Markdown document (i.e., the resulting HTML, PDF or DOCX file) to a previous version.
Yet, a particular advantage of using `reproducibleR` chunks is that users have a fine-grained control over the stages of a data analysis or any other computation that should be checked for reproducibility. 
This allows for forensic examination of non-reproducibility; for example, finding out whether the non-reproducibility is due to changes in the data file, due to the data cleaning or the estimation of a statistical model. 
Using `reproducibleRchunks`, users can separately assess the reproducibility of each stage of a given statistical data analysis (or any other computation).
Also, not all elements of a research asset may be required to reproduce (such as the current date displayed in a presentation of results).
In the following, we will briefly demonstrate how reproduction will be checked and how successful and failed attempts are displayed by the package.
We will go into details of the mechanics of the package, and discuss potential cases of non-reproducibility and how the package will support researchers in handling these cases.
